---
title: "Hotel"
author: "Uğur Dar"
date: "28 03 2020"
output: pdf_document
---
### Libraries

```{r}
library(knitr)
library(tidyverse)
library(ROCR)
library(verification)
```


### Import the data

```{r}
data <- read_csv("hotel_bookings.csv")
```

\newpage

# EDA

```{r}
glimpse(data)
```

\newpage


```{r}
ggplot(data,aes(x=factor(hotel))) +
  geom_bar(col ="black",fill="#993333",alpha=0.5) +
  theme(axis.text.x = element_text(face="bold", size=10)) +
  scale_x_discrete("Hotel") +
  scale_y_continuous("Count")
```

\newpage


```{r}
ggplot(data,aes(factor(arrival_date_month,levels=month.name))) +
  geom_bar(col ="black",fill="#993333",alpha=0.5) +
  theme(axis.text.x = element_text(face="bold", size=8, angle=30)) +
  scale_y_continuous("Count",limits = c(0,15000),breaks=seq(0,15000,by=1500)) +
  scale_x_discrete("Month")
```

```{r}
d <- data %>% 
  group_by(arrival_date_month) %>%
  count() %>%
  arrange(match(arrival_date_month,month.name))
d <- data.frame(ArrivalDateMonth = d$arrival_date_month,N =d$n);kable(d)
```

\newpage

```{r}
ggplot(data = data,aes(factor(is_canceled)))+
  geom_bar( col='black', fill="#993333", alpha = 0.5) +
  facet_wrap(~hotel) +
  scale_x_discrete("Canceled",labels = c("No","Yes")) +
  scale_y_continuous("Count",limits = c(0,50000),breaks=seq(0,47222,by=5000))  +
  theme(axis.text.x = element_text(face="bold", size=10))
```

```{r}
canceledRate <- data %>%
  group_by(Hotel = hotel) %>%
  summarise(CanceledAverage = mean(is_canceled)) 
canceledRate <- as.data.frame(canceledRate)
kable(canceledRate)
```

\newpage

```{r}
ggplot(data = data, aes(x = factor(is_canceled), y = lead_time  )) + 
  geom_boxplot(col='black', fill="#993333", alpha = 0.5) +
  theme(axis.text.x = element_text(face="bold", size=10)) +
  scale_y_continuous("Lead Time",limits = c(0,800),breaks=seq(0,800,by=100)) +
  scale_x_discrete("Canceled",labels = c("No","Yes")) 
```



\newpage


# Model Building

## Missing Values

```{r}
data <- na.omit(data) # I just delete all of them.
```

## Partition data

```{r}
indeks <- sample(2,size = nrow(data), replace = T , prob=c(0.7,0.3))
train <- data[indeks == 1, ]
test <- data[indeks == 2, ]
```

# Logistic Regression

```{r}
set.seed(1234)
glm.fit <- glm(is_canceled ~ hotel + lead_time + arrival_date_month + children +
                        market_segment + is_repeated_guest + adults + babies +
                        previous_cancellations +
                        deposit_type + booking_changes  +
                        reserved_room_type + adr + days_in_waiting_list + customer_type +
                        total_of_special_requests, 
                        data = train , family = "binomial")
summary(glm.fit)

```

\newpage

# Train

## Prediction - Train

```{r}
train_pred <-predict(glm.fit, train,type = 'response')
```

## Cutoff 

```{r}
pred <- prediction(train_pred,train$is_canceled)
perform <- performance(pred,"acc")
max <- which.max(slot(perform,"y.values")[[1]])
prob <- slot(perform,"x.values")[[1]][max]
prob
```


## Accuracy - Train

```{r}
train_pred1 <- ifelse(train_pred >  prob, 1,0)
mean(train$is_canceled == train_pred1) 
```

## Confusion Matrix - Train

```{r}
tble <- table(Actual = train$is_canceled,Predicted = train_pred1 );tble
```

## Classification Table - Train 

```{r}
TN <- tble[1,1]
FN <- tble[2,1]
FP <- tble[1,2]
TP <- tble[2,2]
N <- sum(tble[1,])
P <- sum(tble[2,])
Specificity <- FP/N
Sensitivity <- TP/N
df <- data.frame(Specificity,Sensitivity)
kable(df)
```

## Missclassification Error - Train

```{r}
1 - sum(diag(tble))/sum(tble)
```

## AUC & ROC - Train

### ROC - Train

```{r}
roc.plot(
  train$is_canceled,
  train_pred,
  threshold = seq(0,max(train_pred),0.01)
)
```

### AUC - Train
```{r}
auc <- performance(pred,"auc")
auc <- unlist(slot(auc,"y.values"))
auc
```

\newpage


# Test

## Prediction - Test

```{r}
test_pred <-predict(glm.fit, test,type = 'response')
```


## Accuracy - Test

```{r}
test_pred1 <- ifelse(test_pred > prob , 1,0)
mean(test$is_canceled == test_pred1) 
```

## Confusion Matrix - Test

```{r}
tble1 <- table(Actual = test$is_canceled,Predicted = test_pred1 );tble1
```

## Classification Table - Test 

```{r}
TN <- tble1[1,1]
FN <- tble1[2,1]
FP <- tble1[1,2]
TP <- tble1[2,2]
N <- sum(tble[1,])
P <- sum(tble[2,])
Specificity <- FP/N
Sensitivity <- TP/N
df <- data.frame(Specificity,Sensitivity)
kable(df)
```

\newpage

## Missclassification Error - Test

```{r}
1 - sum(diag(tble1))/sum(tble1)
```

## AUC & ROC - Test

### ROC - Test
```{r}
roc.plot(
  test$is_canceled,
  test_pred,
  threshold = seq(0,max(test_pred),0.01)
)
```

### AUC - Test
```{r}
pred1 <- prediction(test_pred,test$is_canceled)
auc <- performance(pred1,"auc")
auc <- unlist(slot(auc,"y.values"))
auc
```

ROC and AUC are also seems good.
